---
output: github_document
---

# Documentation for the Treasurer

Keep all transactions (income and expenses) in the `accounting.csv` file, with
the date in the ISO 8601 standard format (*YYYY-MM-DD*, all numbers). Income
in the `Income` column, expenses in the `Expense` column. When recording the
incomes and expenses in the `accounting.csv` file, for cheques include the date 
that you wrote the cheque up in the `TransactionDate` column. Once in a while,
compare the transaction dates in the BMO online account with the `accounting.csv`
date. If they are different, update the date using the BMO online account. 
Ultimately, the goal is that the BMO accounting and the GitHub accounting should
be the same.

Receipts should be scanned and placed in the `receipts/` folder, with the
filename as the ISO 8601 date format (`YYYY-MM-DD`), followed by the item and
then the location of purchase. For instance, food purchased on June 5, 2000
would be `2000-06-05-Snacks-Loblaws.pdf`.

Record the relevant details about cheques given out in the `cheques/` folder in 
the `cheques.csv` file. Fill in the appropriate columns. Take a picture of the
cheque with the signatures and save that cheque in the `cheques/images/` folder.
*Important*, **do not** commit these cheque images in the Git repository. They 
should not be publicly viewable. Git ignores all files in the `cheques/images/`
folder.

Given that this is a *coders* group, all summaries of the finances are done in R
with R Markdown. *Occasionally* this document will need to be re-knitted to reflect
an accurate portrayal of the financial situation of the UofTCoders.

# Accounting overview

All calculations were performed using R. For the code, please see the `README.Rmd`
file.

```{r setup, warning=FALSE, message=FALSE, echo=FALSE}
# Load the packages and data.
library(dplyr)
library(lubridate)
library(scales)
knitr::opts_chunk$set(echo = FALSE)
cad <- dollar_format(negative_parens = TRUE)
finances <- read.csv('accounting.csv') %>% 
    mutate(TransactionDate = ymd(TransactionDate))
```

## Actual income and expenses

```{r cashFlow}
income <- sum(finances$Income, na.rm = TRUE)
expense <- sum(finances$Expense, na.rm = TRUE)

library(tidyr)
data_frame(
    Income = cad(income),
    Expense = cad(expense),
    `**Total**` = cad(income - expense)
    ) %>%
    gather(Type, Amount) %>%
    knitr::kable()
```

```{r expensePerWeek}
snacks <- filter(finances, grepl('Snacks', Reason)) 
weeks <- difftime(Sys.Date(), min(snacks$TransactionDate), units = 'weeks')
weeks <- as.numeric(weeks)
per_week <- abs(sum(snacks$Expense) / weeks)
```

**Per session (weekly) expense for snacks**: `r cad(per_week)`

## Projected income and expenses

Values surrounded by brackets `()` denote negative values, as is often done
in accounting. Projected values are until end of *fiscal year*. Fiscal year
starts from the month we first started using the BMO bank account (May): 

Fiscal year: *May 1st-April 30th.*

```{r}
# This needs date needs to be changed each year.
fiscal_year_end <- difftime('2018-05-01', Sys.Date(), units = 'weeks')
fiscal_year_end <- as.numeric(fiscal_year_end)

workshop_income <- finances %>% 
    filter(Tag == "SWC", !is.na(Income), !grepl("walk-in", Reason))

estimated_per_workshop_income <- workshop_income %>% 
    summarize(EstimatedIncome = sum(Income) / length(Income))
estimated_workshops_per_year <- 1

budget_estimate <- data_frame(
    Snacks = -per_week * (fiscal_year_end),
    Misc = -200, # such as stickers, equipment, etc
    Workshops = estimated_per_workshop_income[[1]] * estimated_workshops_per_year
    ) %>%
    mutate(Total = rowSums(.)) %>%
    mutate_all(funs(cad)) %>%
    gather(Item, Amount) %>% 
    as.data.frame() # fix error with pander

library(pander)
pander(budget_estimate, emphasize.strong.rows = nrow(budget_estimate), 
       style = 'rmarkdown', justify = c('left', 'right'))
```
