---
output: 
    md_document:
        variant: markdown_github
---

# Documentation for the Treasurer

Keep all transactions (income and expenses) in the `accounting.csv` file, with
the date in the ISO 8601 standard format (*YYYY-MM-DD*, all numbers). Income
should be positive, expenses should be negative (with a minus `-` sign in front).

Receipts should be scanned and placed in the `receipts/` folder, with the
filename as the general item first followed by the ISO 8601 date format. For
instance, food purchased on June 5, 2000 would be `food-2000-06-05.pdf`.

Given that this is a *coders* group, all summaries of the finances are done in R
with R Markdown. Code is included in the output.

# Accounting overview

```{r setup, warning=FALSE, message=FALSE}
# Load the packages and data.
library(dplyr)
library(tidyr)
library(pander)
finances <- read.csv('accounting.csv') %>% 
    mutate(Date = lubridate::ymd(Date))
```

## Actual income and expenses

**Total funds remaining**: $`r sum(finances$Transaction)`

```{r cashFlow}
finances %>% 
    mutate(Type = ifelse(Transaction < 0, 'Expense', 'Income')) %>% 
    group_by(Type) %>% 
    summarise(Amount = sum(Transaction)) %>% 
    arrange(desc(Type)) %>% 
    knitr::kable()
```

```{r expensePerWeek}
perWeekExpense <- finances %>% 
    filter(Transaction < 0) %>% {
        NumberWeeks <- as.numeric(difftime(Sys.Date(), min(.$Date), units = 'weeks'))
        PerWeekExpense <- sum(.$Transaction) / NumberWeeks
        abs(round(PerWeekExpense, 2))
    }
```

**Per session (weekly) expense**: $`r perWeekExpense`

## Projected income and expenses

```{r}
estimatedBudget <- 
    data.frame(
        IncomeSWC = sum(c(364, 690.40, 655.20)),
        FoodSWC = -sum(c(40 * 10, 20 * 10, 40 * 10)),
        ## Not all weeks will there be a meet up (e.g. Christmas, random weeks).
        CodersSnacks = -perWeekExpense * (52 - 3 - 2) # num of total weeks
    ) %>%
    mutate(Total = rowSums(.)) %>%
    gather(Item, Amount)

pander(estimatedBudget, emphasize.strong.rows = nrow(estimatedBudget), 
       style = 'rmarkdown', justify = c('left', 'right'))
```




